Oregon_Wildfire_full

### 2017-03-02 r_scripts/oregon_clean.rmd
defined new file path
change directory

read_path <- paste0("../data/gan_episodes_of_care.txt")

@@

## 10. Pos (Urgent and Emergency) NA: 2974
```{r}
pos_key <- read_excel("../instructions/LT_pos.xlsx")

>>>>

read_path <- paste0("../../../data/data_original/gan_episodes_of_care.txt")

@@

## 10. Pos (Urgent and Emergency) NA: 2974
```{r}
pos_key <- read_excel("../LT_pos.xlsx")
